%----------------------------------------------------------------------------------------
%	SECOND PAGE: Experience and rest of CV
%----------------------------------------------------------------------------------------

{\fontsize{10pt}{11pt}\selectfont
\begin{rSection}{Professional Experience}

\begin{rSubsection}{Senior Full Stack Software Engineer, Digital Assets Platform}{07.2024 - Ongoing}{Novel Labs Ltd, Switzerland}{Digital Assets}
\item Leading the design and development of a platform supporting digital asset issuance, transaction workflows, and user-facing applications. Responsible for frontend systems, backend systems, and infrastructure. Collaborating closely with product and growth teams to improve system adoption, reliability, and scalability.

- Frontend development
- Backend development
- API and service integration
- Smart contracts development
- Data modeling
- Web3 user-driven transaction workflows
- DevOps, and CI/CD automation
- Security-focused code reviews and internal audits
\end{rSubsection}

%------------------------------------------------
 
\begin{rSubsection}{Security Engineer, Smart Contracts and Architectures}{07.2024 - 10.2024}{Nethermind Ltd, Switzerland}{Web3 Security Consulting}
\item Focused on auditing of financial smart contract systems used in production. Performed deep technical analysis of DeFi protocols and contributed to professional audit reports.

- Code review and vulnerability discovery in financial smart contracts
- Analysis of failure modes, attack surfaces, and protocol-level risks
- Collaboration with senior engineers on audit methodology and report delivery
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Full Stack Software Engineer, Trading and Asset Management Systems}{09.2022 - 06.2024}{Clearstar Labs AG, Switzerland}{Asset Management}
\item Designed and implemented systems for real-time market analytics and automated asset management, spanning user-facing applications, backend services, and data pipelines. Built resilient APIs, data ingestion workflows, monitoring solutions, and interactive dashboards integrating multiple external data sources to support analytical insights and automated decision-making.

- Frontend development
- Backend API development
- Data ingestion and processing pipelines
- Real-time and batch data workflows
- Web3 transactional system implementation
- Data platform design and development
- Smart contracts development
- Automation systems for trading
- Cloud infrastructure and DevOps
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Research Engineer, Distributed Ledgers and Health Data Systems}{01.2022 - 08.2022}{Ontology Engineering Group, Spain}{Applied Research}
\item Conducted applied research on secure, decentralized data sharing architectures in collaboration with industry partners. Designed and prototyped systems combining distributed ledgers, smart contract–based access control, and privacy-preserving data storage to enable controlled health data sharing across heterogeneous infrastructures.

- Distributed data system and architecture design
- Smart contract development for access control and authorization policies
- Secure and privacy-preserving data sharing mechanisms
- Research prototyping and technical documentation
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Full Stack Software Engineer, Digital Health and Data Platforms}{01.2021 - 08.2022}{DIGIT srl, Italy}{Tech Consulting}
\item Led the design, development, and deployment of a cross-platform mobile application and its supporting backend data platform for health and postural stability analysis, including data collection, processing, and visualization, while addressing GDPR requirements related to data privacy, user consent, and secure data handling.

- Cross-platform mobile application development (Android/iOS)
- Backend service development
- Health data collection and processing pipelines
- Cloud infrastructure and DevOps
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Backend Software Engineer and Data Engineering}{2019.09 - 2020.12}{IMAR srl, Italy}{Manufacturing}
\item Developed business intelligence solutions and data processing systems to enable data-driven decision-making. Designed data collection workflows and analytical models to estimate consumer behavior, preferences, and demand forecasts.

- Data engineering and analytics pipelines
- Business intelligence systems
- Applied machine learning for consumer behavior analysis
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Junior Software Engineer, Data Platforms}{03.2017 - 09.2017}{NETLEVEL srl, Italy}{Insurance and Banking}
\item First professional experience in the insurance and banking sector, contributing to the design, implementation, and maintenance of enterprise data platforms. Focused on database architecture, data integrity, performance optimization, and system reliability in a regulated production environment.

- Database design, development, optimization, and maintenance
- Backend development
\end{rSubsection}

\end{rSection}
}

%----------------------------------------------------------------------------------------
%	RESEARCH PUBLICATIONS
%----------------------------------------------------------------------------------------
\newpage
\begin{rSection}{Research Publications} \itemsep -2pt
    \item \textbf{Bigini, G.} (2023). \textit{The InterPlanetary Health Layer}. PhD Thesis.
    \item \textbf{Bigini, G.}, Zichichi, M., Lattanzi, E., Ferretti S., \& D'Angelo G. (2023). \textit{On the Decentralization of Health Systems for Data Availability: a DLT-based Architecture}. IEEE CCNC, 372-377.
    \item \textbf{Bigini, G.}, \& Lattanzi, E. (2022). \textit{Toward the Interplanetary Health Layer for the Internet of Medical Things with Distributed Ledgers and Storages}. IEEE Access, 82883-82895.
    \item \textbf{Bigini, G.}, Zichichi, M., Lattanzi, E., Ferretti S., \& D'Angelo G. (2022). \textit{Decentralized Health Data Distribution: A DLT-based Architecture}. IEEE Blockchain, 97-104.
    \item \textbf{Bigini, G.}, Freschi, V., Bogliolo, A., \& Lattanzi, E. (2021). \textit{Decentralising the Internet of Medical Things with DLT and Off-Chain Storages}. Springer GOODTECHS, 80-90.
    \item \textbf{Bigini, G.}, Freschi, V., \& Lattanzi, E. (2020). \textit{A Review on Blockchain for the Internet of Medical Things}. Future Internet, 12(12):208, MDPI.
\end{rSection}

%----------------------------------------------------------------------------------------
\iffalse
\begin{rSection}{Academic Publications} \itemsep -2pt
    \item \textbf{Bigini, G.} (2023).
    \textit{The InterPlanetary Health Layer}. \textbf{PhD Thesis}.
    
    \item \textbf{Bigini, G.}, Zichichi, M., Lattanzi, E., Ferretti S., \& D'Angelo G. (2023).
    \textit{On the Decentralization of Health Systems for Data Availability: a DLT-based Architecture}. \textbf{IEEE}.
    \item \textbf{Bigini, G.}, \& Lattanzi, E. (2022).
    \textit{Toward the Interplanetary Health Layer for the Internet of Medical Things with Distributed Ledgers and Storages}. \textbf{IEEE}.
    
    \item \textbf{Bigini, G.}, Zichichi, M., Lattanzi, E., Ferretti S., \& D'Angelo G. (2022).
    \textit{Decentralized Health Data Distribution: A DLT-based Architecture for Data Protection}. \textbf{IEEE}
    
    \item \textbf{Bigini, G.}, Freschi, V., Bogliolo, A., \& Lattanzi, E. (2021).
    \textit{Decentralising the Internet of Medical Things with Distributed Ledger Technologies and Off-Chain Storages: a Proof of Concept}. \textbf{Springer}.
    
    \item \textbf{Bigini, G.}, Freschi, V., \& Lattanzi, E. (2020).
    \textit{A Review on Blockchain for the Internet of Medical Things: Definitions, Challenges, Applications, and Vision}. \textbf{MDPI}.
\end{rSection}
\fi

%----------------------------------------------------------------------------------------

\iffalse
\begin{rSection}{CERTIFICATES} \itemsep -2pt

    \begin{rSubsection}{Doctor Europaeus International Honorary Title}{05.2023}{University of Urbino, Urbino, Italy}{}
    \end{rSubsection}
    \vspace{-5pt}
    \begin{rSubsection}{EIT Digital Certificate eHealth Personalised Prevention}{08.2020}{TalTech, Tallin, Estonia}{}
    \end{rSubsection}
    \vspace{-5pt}    
    \begin{rSubsection}{EIT Digital ICT Double Degree Diploma in Data Science}{10.2019}{EIT Digital, Berlin, Germany}{}
    \end{rSubsection}
    \vspace{-5pt}
    \begin{rSubsection}{EIT Digital Certificate Internet of Things and Business Transformation}{08.2018}{KTH/Ericsson, Stockholm, Sweden}{}
    \end{rSubsection}    
\end{rSection}

\begin{rSection}{Activities} \itemsep -2pt
    
    \begin{rSubsection}{Nethermind PhD Apprenticeship}{07.2024 - 10.2024}{Nethermind, London, UK}{}
    \end{rSubsection}
    \vspace{-5pt}   
    \begin{rSubsection}{Visiting Researcher}{01.2022 - 08.2022}{Universidad Politécnica de Madrid, Madrid, Spain}{}
    \end{rSubsection}
    \vspace{-5pt}    
    \begin{rSubsection}{University Project in Collaboration with IBM - Fake News Detection}{01.2018 - 06.2018}{IBM Segrate, Milan, Italy}{}
    \end{rSubsection}
    \vspace{-5pt}    
    \begin{rSubsection}{Erasmus+ Traineeship - Gamification}{06.2016 - 09.2016}{Disruptive Media Learning Lab, Coventry, UK}{}
    \end{rSubsection}
    \vspace{-5pt}    
    \begin{rSubsection}{Erasmus+ Exchange}{09.2015 - 02.2016}{Universidad Complutense de Madrid, Madrid, Spain}{}
    \end{rSubsection}

\end{rSection}
\fi

%----------------------------------------------------------------------------------------

\iffalse
\begin{rSection}{Languages} \itemsep -2pt

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Italian &  Fluent \\
English &  Fluent \\
Spanish &  Fluent \\
German  &  Beginner \\
\end{tabular}

\end{rSection}
\fi
